Working title: Mirkovi\'c--Vybornov fusion in Beilinson--Drinfeld Grassmannian

### 2020-12-26 examples.tex
typos

    I have used the relations Roger found (and I checked) $a = 0$ and $cs - bd = 0$ above.

    To sum up the pair of matrices above should contain the same information as the matrix from the previous example 
    \[
    \begin{bmatrix}
    0 & 1 \\
      & 0 & 1 \\
      &   & 0 & 1 \\
      &   &   & s &  & b & c \\
      &   &   &   & 0 & 1 & 0 \\
      &   &   &   & 0 & s & d \\
      &   &   &   &   &   & 0
    \end{bmatrix} \Leftrightarrow \left( \begin{bmatrix}
            0 & 1\\
              & 0 & 1\\
              &   & 0 &  &  \\
              & & & 0 & \frac d {t-s} \\
              & & & & 0  
        \end{bmatrix} , \begin{bmatrix}
        s & \frac b {t^2} \\ & s 
        \end{bmatrix}\right) 
    \] 
\end{example}

{\bf Wish.} Given $L$ in $\Grbd$ define a map to $T_\mu$ just like MVy by taking $[t\big|_{L_0/L}]$ and use the fact that $[t\big|_{L_0/L_i]$ for $i = 1,2$ are companion matrices of the right type/piece together two MVy isomorphisms to make a BD MVy iso.

Lin alg question: if $p(t,t-s) = p_1(t)p_2(t-s)$ how are $C(p_1),C(p_2),C(p)$ related. I think it's basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}

>>>>

    I have used the relations Roger found (and I checked) $a = 0$ and $cs - bd = 0$ in the calculations above.

    To sum up, the pair of matrices above should contain the same information as the matrix from the previous example 
    \[
    \begin{bmatrix}
    0 & 1 \\
      & 0 & 1 \\
      &   & 0 & 1 \\
      &   &   & s &  & b & c \\
      &   &   &   & 0 & 1 & 0 \\
      &   &   &   & 0 & s & d \\
      &   &   &   &   &   & 0
    \end{bmatrix} \Leftrightarrow \left( \begin{bmatrix}
            0 & 1\\
              & 0 & 1\\
              &   & 0 &  &  \\
              & & & 0 & \frac d {t-s} \\
              & & & & 0  
        \end{bmatrix} , \begin{bmatrix}
        s & \frac b {t^2} \\ & s 
        \end{bmatrix}\right) 
    \] 
\end{example}

{\bf Wish.} Given $L$ in $\Grbd$ define a map to $T_\mu$ just like MVy by taking $[t\big|_{L_0/L}]$ and use the fact that $[t\big|_{L_0/L_i}]$ for $i = 1,2$ are companion matrices of the right type, piece together two MVy isomorphisms to make a BD MVy iso.

Equivalent lin alg question: If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related? I think it's basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}
